%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% A clean template for an academic CV
%
% Uses tabularx to create two column entries (date and job/edu/citation).
% Defines commands to make adding entries simpler.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt, a4paper]{article}

% Full Unicode support for non-ASCII characters
\usepackage[utf8]{inputenc}

% Useful aliases
\newcommand{\UT}{University of Tartu}
\newcommand{\UTGEO}{Department of Geology}
\newcommand{\UA}{University of Alberta}
\newcommand{\UAEAS}{Department of Earth and Atmospheric Sciences}

% Identifying information
\newcommand{\Title}{Curriculum Vit\ae}
\newcommand{\FirstName}{Kaarel}
\newcommand{\LastName}{Mänd}
\newcommand{\Initials}{K}
\newcommand{\MyName}{Dr. \FirstName\ \LastName}
\newcommand{\Me}{\textbf{\LastName, \Initials}}  % For citations
\newcommand{\Email}{kaarel.mand@ut.ee}
\newcommand{\PersonalWebsite}{kaarelmand.github.io}
\newcommand{\ETIS}{www.etis.ee/CV/Kaarel\_Mand}
\newcommand{\ORCID}{0000-0003-1575-3710}
\newcommand{\Address}{
  University of Tartu \\ Department of Geology \\ Ravila 14A \\ Tartu 50411 \\ Estonia
}

% Names for citing coauthors
\newcommand{\Arps}{Kirsimäe, K}
\newcommand{\Kart}{Paiste, K}
\newcommand{\Parn}{Paiste, P}
\newcommand{\Aivo}{Lepland, A}
\newcommand{\Kurt}{Konhauser, KO}
\newcommand{\Weid}{Hao, W}
\newcommand{\Dan}{Alessi, DS}
\newcommand{\Bau}{Bau, M}
\newcommand{\Tony}{Prave, AR}
\newcommand{\Tim}{Kreistmann, T}
\newcommand{\Sasha}{Romashkin, AE}
\newcommand{\Yul}{Deines, YE}
\newcommand{\Jake}{Bailey, JV}
\newcommand{\Karen}{Bakakas, K}
\newcommand{\Stef}{Lalonde, SV}
\newcommand{\Jamie}{Robbins, LJ}
\newcommand{\Marie}{Thoby, M}
\newcommand{\Sus}{Porter, SM}
\newcommand{\Noah}{Planavsky, NJ}
\newcommand{\Chris}{Reinhard, CT}
\newcommand{\Dave}{Fike, DA}
\newcommand{\Aub}{Zerkle, AL}
\newcommand{\MWil}{Williams, MJ}
\newcommand{\Dylan}{Wilmeth, DT}
\newcommand{\Kim}{Myers, KD}
\newcommand{\Mark}{van Zuilen, MA}
\newcommand{\Bos}{Wing, B}
\newcommand{\Hao}{Yan, H}

% Template configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Disable hyphenation
\usepackage[none]{hyphenat}

% Control the font size
\usepackage{anyfontsize}

% Icon fonts (requires using xelatex or luatex)
\usepackage[fixed]{fontawesome5}
\usepackage{academicons}

% Template variables for styling
\newcommand{\TablePad}{\vspace{-0.4cm}}
\newcommand{\SoftwareTitle}[1]{{\bfseries #1}}
\newcommand{\TableTitle}[1]{{\fontsize{12pt}{0}\selectfont \itshape #1}}

% For fancy and multipage tables
\usepackage{tabularx}
\usepackage{ltablex}

% Define a new environment to place all CV entries in a 2-column table.
% Left column are the dates, right column the entries.
\usepackage{environ}
\NewEnviron{EntriesTable}{
\TablePad
\begin{tabularx}{\textwidth}{@{}p{0.12\textwidth}@{\hspace{0.02\textwidth}}p{0.86\textwidth}@{}}
  \BODY
\end{tabularx}
}

% Macros to add links and mark publications
\newcommand{\DOI}[1]{\newline DOI: \aiDoi\ \href{https://doi.org/#1}{#1}}
\newcommand{\DOILink}[1]{\href{https://doi.org/#1}{doi.org/#1}}
\newcommand{\Website}[1]{\href{https://#1}{#1}}
\newcommand{\Preprint}[1]{\newline Preprint: \faFilePdf\ \DOILink{#1}}
\newcommand{\Youtube}[1]{\newline Recording: \faYoutube\, \href{https://www.youtube.com/watch?v=#1}{youtube.com/watch?v=#1}}
\newcommand{\GitHub}[1]{\newline Code: \faGithub\ \href{https://github.com/#1}{github.com/#1}}
\newcommand{\Role}[1]{\newline Role: \faUsers\ #1}
\newcommand{\Slides}[1]{\newline Slides: \faTv\ \href{https://#1}{#1}}
\newcommand{\Poster}[1]{\newline Poster: \faTv\ \href{https://#1}{#1}}
\newcommand{\Abstract}[1]{\newline Abstract: \faFile\ \Website{#1}}
\newcommand{\SlidesShort}[2]{\newline Slides: \faTv\ \href{https://#1}{#2}}
\newcommand{\PosterShort}[2]{\newline Poster: \faTv\ \href{https://#1}{#2}}
\newcommand{\AbstractShort}[2]{\newline Abstract: \faFile\ \href{https://#1}{#2}}
\newcommand{\SlidesDOI}[1]{\newline Slides: \faTv\ \DOILink{#1}}
\newcommand{\PosterDOI}[1]{\newline Poster: \faImage\ \DOILink{#1}}
\newcommand{\AbstractDOI}[1]{\newline Abstract: \faFile\ \DOILink{#1}}
\newcommand{\OA}{\aiOpenAccess\enspace}

% Macros to set the year and duration on the left column
\newcommand{\Duration}[2]{\fontsize{9pt}{0}\selectfont #1 -- #2}
\newcommand{\Year}[1]{\fontsize{9pt}{0}\selectfont #1}
\newcommand{\Ongoing}{present}
\newcommand{\Future}{Future}
\newcommand{\Appointment}[4]{\textbf{#1} \newline #2 \newline #3}

% Define command to insert month name and year as date
\usepackage{datetime}
\newdateformat{monthyear}{\monthname[\THEMONTH], \THEYEAR}

% Set the page margins
\usepackage[a4paper,margin=1.5cm,includehead,headsep=5mm]{geometry}

% To get the total page numbers (\pageref{LastPage})
\usepackage{lastpage}

% No indentation
\setlength\parindent{0cm}

% Increase the line spacing
\renewcommand{\baselinestretch}{1.2}
% and the spacing between rows in tables
\renewcommand{\arraystretch}{1.5}

% Remove space between items in itemize and enumerate
\usepackage{enumitem}
\setlist{nosep}

% Use custom colors
\usepackage[usenames,dvipsnames]{xcolor}

% Set fonts (requires compilation with xelatex)
\usepackage{fontspec}
\setmainfont[%
  Path = fonts/notoserif/,
  UprightFont = NotoSerif-Regular,
  BoldFont = NotoSerif-Bold,
  ItalicFont = NotoSerif-Italic,
  Extension = .ttf
]{NotoSerif}



% Set the spacing for sections
\usepackage{titlesec}
\titleformat{\section}
  {\normalfont\Large\mdseries} % format
  {} % label
  {0pt} % separation (left separation for hang)
  {} % text before title
  [\titlerule] % text after title
\titleformat{\subsection}
  {\normalfont\large\mdseries} % format
  {} % label
  {0pt} % separation (left separation for hang)
  {} % text before title

% Disable number of sections. Use this instead of "section*" so that the sections still
% appear as PDF bookmarks. Otherwise, would have to add the table of contents entries
% manually.
\makeatletter
\renewcommand{\@seccntformat}[1]{}
\makeatother

% Set fancy headers
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\lhead{\fontsize{9pt}{10pt}\selectfont
  \monthyear\today
}
\chead{
  \fontsize{9pt}{10pt}\selectfont
  \MyName
  \hspace{0.2cm} -- \hspace{0.2cm}
  \Title
}
\rhead{\fontsize{9pt}{10pt}\selectfont \thepage{} of \pageref*{LastPage}}
\renewcommand{\headrulewidth}{0pt}

% Metadata for the PDF output and control of hyperlinks
\usepackage[colorlinks=true]{hyperref}
\hypersetup{
  pdftitle={\MyName\ - \Title},
  pdfauthor={\MyName},
  linkcolor=blue,
  citecolor=blue,
  filecolor=black,
  urlcolor=MidnightBlue
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

% No header for the first page
\thispagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.7\textwidth}
{\fontsize{22pt}{0}\selectfont\MyName}
\end{minipage}
\begin{minipage}[t]{0.3\textwidth}
  \begin{flushright}
    Last updated: \monthyear\today
  \end{flushright}
\end{minipage}
\\[-0.1cm]
\rule{\textwidth}{2pt}
\\[0.1cm]
\begin{minipage}[t]{0.7\textwidth}
    Email: \href{mailto:\Email}{\Email}
    \\
    ORCID: \href{https://orcid.org/\ORCID}{\ORCID}
    \\
    Website: \Website{\PersonalWebsite}
    \\
    ETIS: \Website{\ETIS}
\end{minipage}
\begin{minipage}[t]{0.3\textwidth}
  \begin{flushright}
    \Address
  \end{flushright}
\end{minipage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Professional Appointments}

\begin{EntriesTable}
  \Duration{2020}{\Ongoing}  &
  \textbf{Research Fellow}
  \newline
  \emph{\UT, \UTGEO, Estonia}
  \\
  \Duration{2018}{2019}  &
  \textbf{Teaching Assistant}
  \newline
  \emph{\UA, \UAEAS, Canada}
  \\
  \Duration{2018}{2020}  &
  \textbf{Peer Writing Tutor}
  \newline
  \emph{\UA, Centre for Writers, Canada}
  \\
  \Duration{2016}{2020}  &
  \textbf{Environmental Chemistry Specialist}
  \newline
  \emph{\UT, \UTGEO, Estonia}
  \\
  \Duration{2013}{2015}  &
  \textbf{Laboratory Assistant}
  \newline
  \emph{\UT, \UTGEO, Estonia}
\end{EntriesTable}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}

\begin{EntriesTable}
  \Duration{2016}{2021}  &
  \textbf{PhD in Geochemistry}
  \newline
  \emph{\UA, \UAEAS, Canada}
  \newline
  Supervisors: Kurt O. Konhauser, Aivo Lepland, Kalle Kirsimäe
  \\
  \Duration{2014}{2016}  &
  \textbf{MSc in Geology} \emph{cum laude}
  \newline
  \emph{\UT, \UTGEO, Estonia}
  \newline
  Supervisor: Kalle Kirsimäe
  \\
  \Duration{2010}{2013}  &
  \textbf{BSc in Geology} \emph{cum laude}
  \newline
  \emph{\UT, \UTGEO, Estonia}
  \newline
  Supervisor: Kalle Kirsimäe
\end{EntriesTable}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Grants \& Funded Projects}

\begin{EntriesTable}
  \Duration{2020}{2023}  &
  Estonian Research Council: "\textbf{Vanadium distribution and compounds in Tremadocian black shale and potential extraction technologies}." PI: Rutt Hints. \emph{Tallinn University of Technology, \UT}. Grant ID: \href{https://www.etis.ee/Portal/Projects/Display/01ce0ae7-decb-43a9-a55a-49a7c75654bd?lang=ENG}{ResTA18}.
  \\
  \Duration{2016}{2021}  &
  Ministry of Education and Research of the Republic of Estonia, Archimedes Foundation: \textbf{Kristjan Jaak Scholarship for doctoral study abroad}. \FirstName \ \LastName, for study at \UA, Canada.
\end{EntriesTable}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Awards \& Honors}

\begin{EntriesTable}
  \Duration{2019}{2020}  &
  \textbf{Ashley \& Janet Cameron Graduate Scholarship}
  \newline
  \emph{UAlberta North, \UA, Canada}
  \\
  \Year{2019}  &
  \textbf{Graduate Fellowship}
  \newline
  \emph{\UA, Canada}
  \\
  ~  &
  \textbf{Graduate Student Teaching Award}
  \newline
  \emph{\UA, Canada}
  \\
  \Year{2018}  &
  \textbf{Vega Graduate Scholarship}
  \newline
  \emph{\UA, Canada}
  \\
  ~  &
  \textbf{Harington Paleoenvironmental Scholarship}
  \newline
  \emph{\UA, Canada}
  \\
  ~  &
  \textbf{Steve and Elaine Antoniuk Graduate Scholarship} in Arctic Research in Earth and Atmospheric Sciences
  \newline
  \emph{\UA, Canada}
  \\
  \Duration{2016}{2020}  &
  \textbf{Doctoral Recruitment Scholarship}
  \newline
  \emph{\UA, Canada}
  \\
  \Year{2014}  &
  National Contest for University Students: \textbf{1st prize in Bio- and Environmental Science} (undergraduate level)
  \newline
  \emph{Estonian Research Council, Estonia}
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Academic Service}

\subsection{Administration}
\begin{EntriesTable}
  \Duration{2021}{\Ongoing}  &
  Erasmus+ Departmental Coordinator
  \newline
  Negotiating inter-university agreements, evaluating student applications.
  \newline
  \emph{\UTGEO, \UT}
\end{EntriesTable}

\subsection{Committees}

\begin{EntriesTable}
  \Year{\Future} &
  Undergraduate Student Admissions Committee
  \newline
  \emph{\UTGEO, \UT}
  \\
  ~ &
  Master's Dissertation Examination Committee
  \newline
  \emph{\UTGEO, \UT}
  \\
  \Duration{2022}{\Ongoing} &
  Vision and Integration Committee of the Institute of Ecology and Earth Sciences
  \newline
  Conference organization, student advocacy, ecological advocacy.
  \newline
  \emph{\UT}
  \Year{2020}
\end{EntriesTable}

\subsection{Reviewer}

\begin{itemize}
  \item Science
  \item Nature Communications
  \item Proceedings of the National Academy of Sciences
  \item Earth and Planetary Science Letters
  \item Chemical Geology
  \item Precambrian Research
  \item Canadian Journal of Earth Sciences
  \item Estonian Journal of Earth Sciences
\end{itemize}

\subsection{Examiner}

\begin{EntriesTable}
  \Year{2021} &
  MSc dissertation examiner (Nanyun Zhang)
  \newline
  \emph{\UT, Institute of Chemistry}
  \\
  ~ &
  BSc dissertation examiner (Maria Ojap)
  \newline
  \emph{\UT, \UTGEO}
\end{EntriesTable}

\subsection{Conferences}

\begin{EntriesTable}

\Year{2021} &
  Schola Geologica XVII
  \newline
  Session chair.
  \newline
  \emph{Tartu, Estonia}
  \\
\Year{2020} &
  Northern Research Day 2020
  \newline
  Oral presentation awards adjucator.
  \newline
  \emph{Edmonton, AB, Canada}
  \\
\Year{2019} &
  2nd Geobiology Society Conference 
  \newline
  Session chair and co-organizer.
  \newline
  \emph{Banff, AB, Canada}
  \\
\Year{2017} &
  1st Geobiology Society Conference
  \newline
  Co-organizer.
  \newline
  \emph{Banff, AB, Canada}
\end{EntriesTable}

\subsection{Open-Source Software}

\begin{EntriesTable}
  \Duration{2020}{\Ongoing}  &
  \textbf{pyrolite} | \Website{https://pyrolite.readthedocs.io/en/main/}
  \newline
  A set of tools for getting the most from your geochemical data. 
  \Role{Code contributor}
  \GitHub{morganjwilliams/pyrolite}
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Teaching \& Mentorship}

\subsection{Courses}

\begin{EntriesTable}
  \Duration{2021}{\Ongoing}  &
  LTOM.03.006: \textbf{Isotope Geochemistry and Geochemical Modelling}
  \newline
  Teaching the module on transition metal isotopes.
  \newline
  \textit{\UT, Estonia}
  \\
  \Duration{2018}{2019}  &
  EA100: \textbf{Planet Earth}
  \newline
  Lab instructor and examiner for two lab groups (40 students per year).
  \newline
  \textit{\UA, Canada}
  \\
  \Year{2018}  &
  EA205: \textbf{Environment Earth}
  \newline
  Teaching the module on earthquakes.
  \newline
  \textit{\UA, Canada}
  \\
  \Year{2014}  &
  LOOM.03.010: \textbf{Field-training of Earth Sciences I}
  \newline
  Field co-instructor.
  \newline
  \textit{\UT, Estonia}
\end{EntriesTable}

\subsection{Supervision}

\begin{EntriesTable}
  \Year{\Future}  &
  \textbf{Bojidar Mandjukov}
  \newline
  Lead PhD advisor.
  \newline
  \emph{\UT, \UTGEO, Estonia}
  \newline
  Co-supervisor: Anthony Chappaz
  \\
  \Year{2019}  &
  \textbf{Baptiste Coutret}
  \newline
  Direct supervisor on BSc thesis and undergraduate internship.
  \newline
  \emph{\UA, Canada; Université de Poitiers, France}
  \newline
  Co-supervisors: Abderrazak El Albani, Kurt O. Konhauser
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Media \& Outreach}

\begin{EntriesTable}
\Year{2022} &
  Interviewed by \textit{Novaator} web portal,
  \textit{``Eesti geoloogid otsivad maapõuest keeruka elu tekke jälgi''}
  (13 April 2022):
  \Website{novaator.err.ee/1608563866}
  \\
\Year{2021}  &
  Interviewed by \textit{Eos} magazine,
  \textit{``Updating Dating Helps Tackle Deep-Time Quandaries''}
  (22 February 2022):
  \href{https://eos.org/features/updating-dating-helps-tackle-deep-time-quandaries}{eos.org/features/updating-dating-helps-tackle-deep-time-quandaries}
  \\
\Year{2020}  &
  Interviewed by \textit{Smithsonian Air \& Space} magazine,
  \textit{``Long-lasting Oxygen in Earth’s Early Atmosphere May Have Jump-Started the Evolution to Animal Life''}
  (19 May 2020):
 \href{https://www.smithsonianmag.com/air-space-magazine/long-lasting-oxygen-earths-early-atmosphere-may-have-jump-started-evolution-animal-life-180974919/}{smithsonianmag.com/air-space-magazine/...}
  \\
~  &
  Interviewed by \textit{Õhtuleht} newspaper,
  \textit{``MILJARDIPARADOKS LAHENEB! Eesti teadlased kirjutavad ümber maakera ajalugu''}
  (12 May 2020):
  \href{https://www.ohtuleht.ee/1001539/miljardiparadoks-laheneb-eesti-teadlased-kirjutavad-umber-maakera-ajalugu}{ohtuleht.ee/1001539}
  \\
~  &
  Interviewed by the radio show \textit{``Labor''} on
  \textit{Vikerraadio}
  (09 May, 2020):
  \href{https://vikerraadio.err.ee/1082611/labor-ohuhapniku-ajalugu-ja-viljakusmolekulid}{vikerraadio.err.ee/1082611/labor-ohuhapniku-ajalugu-ja-viljakusmolekulid}
  \\
~  &
  Interviewed by the radio show \textit{``Alberta Morning News''} on
  \textit{770 CHQR Newstalk}
  (03 May 2020).
  \\
~  &
  Interviewed by \textit{Strana Rosatom: Laboratory} magazine.
  \\
~  &
  Co-published press report on the web portal \textit{Novaator},
  \textit{``Keskikka jõudnud Maa atmosfäär püsis ootamatult hapnikurikas''}
  (19 March 2020):
  \href{https://novaator.err.ee/1065971/keskikka-joudnud-maa-atmosfaar-pusis-ootamatult-hapnikurikas}{novaator.err.ee/1065971}
  \\
~  &
  Co-published press report on the web portal \textit{EurekAlert!},
  \textit{``Study challenges common view of oxygen scarcity on Earth 2 billion years ago''}
  (24 March 2020):
  \href{https://www.eurekalert.org/news-releases/665842}{eurekalert.org/news-releases/665842}
  \\
\Year{2018}  &
  Published press report on the web portal \textit{Science Trends},
  \textit{``Geochemical Methods Help Resolve A Long-Standing Debate In Amber Palaeontology''}
  (17 December 2018):
  \href{https://sciencetrends.com/geochemical-methods-help-resolve-a-long-standing-debate-in-amber-palaeontology/}{sciencetrends.com/...}
  \\
\Year{2015}  &
  Instructor at an outreach day for high-school students as part of the \textit{RGNO2015} oceanographic summer school in Swakompund, Namibia.
  \\
~  &
  Volunteer at \textit{Science Town, Tartu Hanseatic Days} in Tartu, Estonia.
  \\
\Duration{2014}{2015}  &
  Various geoscience recruiting talks and tours for the \UT, \UTGEO, Estonia.
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Presentations}

\begin{EntriesTable}
\Year{2021}  &
  \Me, \Noah, \Sus, \Jamie, Wang, C, \Tim, \Kart, \Parn, \Yul, \Arps, \Aivo, \Kurt.
  Protracted oxygenation in the Paleoproterozoic did not result in proliferation of mitochondrial organisms,
  \emph{Goldschmidt 2021},
  Bordeaux, France (online).
  \AbstractDOI{10.7185/gold2021.6732}
  \\
  ~ &
  \Tim, \Aivo, \Bau, \Tony, \Kart, \Me, \Sasha, \Arps.
  Rare Earth Elements Аnd Carbon Isotope Record from the Carbonates of the Zaonega Formation,
  \emph{Shungite-2020–2021},
  Petrozavodsk, Russia (online).
  \Abstract{elibrary.ru/item.asp?id=46491364}
  \\
  ~ &
  \Kart, \Dave, \Arps, \Me, \Parn, Jones, C, \Aivo, \Tony, \Sasha.
  Testing the Global Significance of the Sulfur Isotope Record of the Paleoproterozoic Zaonega Formation,
  \emph{Shungite-2020–2021},
  Petrozavodsk, Russia (online).
  \Abstract{elibrary.ru/item.asp?id=46491364}
  \\
  ~ &
  \Me.
  The origins of biodiversity: Did changing oxygen levels in the Proterozoic induce the rise of complex life?
  \emph{Seminars on Animal Ecology},
  Tartu, Estonia.
  \SlidesShort{kaarelmand.github.io/publication/mand-2021-originsbiodiversity-did/mand-2021-originsbiodiversity-did.pdf}{kaarelmand.github.io/publication/mand-2021-originsbiodiversity-did}
  \\
  \Year{2020} &
  \Me.
  Kaotatud paradiis ja keeruka elu häll: Hapnik ja päristuumsed 2 miljardit aastat tagasi,
  \emph{Schola Geologica XVI: Living densely together},
  Tartu, Estonia.
  \SlidesShort{https://kaarelmand.github.io/publication/mand-2020-kaotatudparadiisja/mand-2020-kaotatudparadiisja.pdf}{kaarelmand.github.io/publication/mand-2020-kaotatudparadiisja}
  \\
  ~ &
  \Aivo, \Karen, Moussavou, M, \Tim, \Kart, \Me, \Yul, \Sasha, \Tony, \Arps.
  Lomagundi-Jatuli Carbon Isotope Excursion – Isotopic Shift Happens,
  \emph{Goldschmidt 2020},
  Hawaii, USA (online).
  \AbstractDOI{10.46427/gold2020.1460}
  \\
  ~ &
  \MWil, Schoneveld, L, Miller, L, Mao, Y, \Me, Gosses, J, Dalton, H, Bath, A, Barnes, SJ.
  pyrolite: Tools for Data Driven Geochemistry,
  \emph{AGU 2020},
  Online.
  \AbstractShort{ui.adsabs.harvard.edu/abs/2020AGUFMIN040..06W/abstract}{ui.adsabs.harvard.edu/abs/2020AGUFMIN040..06W}
  \\
  ~ &
  \Dylan, \Kim, \Stef, \Me, \Kurt, Grandin, P, \Mark.
  Oxygen and pH gradients within silicifying microbial mats in El Tatio, Chile,
  \emph{Gordon Research Conference “Geobiology 2020”},
  Galveston, Texas, USA.
  \\
  \Year{2019} &
  \Me, \Jamie, \Stef, \Marie, \Kart, \Tim, \Parn, \Chris, \Sasha, \Arps, \Aivo, \Kurt.
  Oxygenated oceans persisted after the Lomagundi Event: evidence from the Zaonega Formation,
  \emph{2nd Geobiology Society Meeting},
  Banff, Alberta, Canada.
  \PosterShort{kaarelmand.github.io/publication/mand-2019-oxygenatedoceanspersisted/mand-2019-oxygenatedoceanspersisted.pdf}{kaarelmand.github.io/publication/mand-2019-oxygenatedoceanspersisted}
  \AbstractShort{cms.eas.ualberta.ca/geobiology2019/wp-content/uploads/sites/28/2019/06/Geobiology-Conference-proceedings.pdf}{cms.eas.ualberta.ca/geobiology2019}
  \\
  ~ &
  \Weid, \Me, Li, Y, \Dan, \Kurt.
  Acid weathering, clay transport and enhanced phosphate supply to early Paleoproterozoic oceans following the Great Oxidation Event,
  \emph{2nd Geobiology Society Meeting},
  Banff, Alberta, Canada.
  \AbstractShort{cms.eas.ualberta.ca/geobiology2019/wp-content/uploads/sites/28/2019/06/Geobiology-Conference-proceedings.pdf}{cms.eas.ualberta.ca/geobiology2019}
  \\
  \Year{2018} &
  \Me, \Marie, \Stef, \Kart, \Jamie, \Aivo, \Arps, \Kurt.
  High molybdenum abundance in the  2 Ga Zaonega Formation: Implications for seawater following the Lomagundi Excursion,
  \emph{Gordon research conference “Geobiology 2018”},
  Galveston, Texas, USA.
  \PosterShort{kaarelmand.github.io/publication/mand-2018-highmolybdenumabundance/mand-2018-highmolybdenumabundance.pdf}{kaarelmand.github.io/publication/mand-2018-highmolybdenumabundance}
  \\
  ~ &
Paiste, K., Lepland, A., Zerkle, A.L., Wing, B.A., Kreitsmann, T., Kirsimäe, K., Izon, G., Mänd, K., Bui, T.H.
  \Kart, \Aivo, \Aub, \Bos, \Tim, \Arps, Izon, G, \Me, Bui, TH.
  Multiple S and Corg isotopes recording environmental changes in the ca. 2Ga Zaonega Fm, Onega Basin, Russia,
  \emph{Gordon research conference “Geobiology 2018”},
  Galveston, Texas, USA.
  \\
  \Year{2017} &
  \Me, \Aivo, \Marie, \Stef, \Kart, \Jamie, \Arps, \Kurt.
  Trace metal enrichment in 1.98 Ga black shales of the Zaonega Formation,
  \emph{1st Geobiology Society Meeting},
  Banff, Alberta, Canada.
  \PosterShort{kaarelmand.github.io/publication/mand-2017-tracemetalenrichment/mand-2017-tracemetalenrichment.pdf}{kaarelmand.github.io/publication/mand-2017-tracemetalenrichment}
  \\
  \Year{2016} &
  \Me, \Jake, \Aivo, \Arps.
  Origin of rod and dumbbell shaped phosphate precipitates in Namibian shelf sediments,
  \emph{32nd Nordic Geological Winter Meeting},
  Helsinki, Finland.
  \SlidesShort{kaarelmand.github.io/publication/mand-2016-originroddumbbell/mand-2016-originroddumbbell.pdf}{kaarelmand.github.io/publication/mand-2016-originroddumbbell}
  \\
  \Year{2015} &
  \Me, \Jake, \Aivo, \Arps.
  Apatitic micronodules in Namibian shelf sediments: Mineralized microbes or diagenetic precipitates?
  \emph{Goldschmidt 2015},
  Prague, Czechia.
  \SlidesShort{kaarelmand.github.io/publication/mand-2015-apatiticmicronodules-namibian/mand-2015-apatiticmicronodules-namibian.pdf}{kaarelmand.github.io/publication/mand-2015-apatiticmicronodules-namibian}
  \Abstract{goldschmidtabstracts.info/abstracts/abstractView?id=2015003584}
  \\
  ~ &
  \Me.
  Phosphatised microstructures in ancient and modern phosphorites,
  \emph{Scientific knowledge applied to the sustainable use of coastal upwelling ecosystems},
  Swakopmund, Namibia.
  \SlidesShort{kaarelmand.github.io/publication/mand-2015-phosphatisedmicrostructuresancient/mand-2015-phosphatisedmicrostructuresancient.pdf}{kaarelmand.github.io/publication/mand-2015-phosphatisedmicrostructuresancient}
  \\
  \Year{2014} &
  \Me.
  Mikrofossiilid maailma vanimates fosforiitides,
  \emph{Schola Geologica X},
  Jäneda, Estonia.
  \SlidesShort{kaarelmand.github.io/publication/mand-2014-mikrofossiilidmaailmavanimates\_/mand-2014-mikrofossiilidmaailmavanimates\_.pdf}{kaarelmand.github.io/publication/mand-2014-mikrofossiilidmaailmavanimates\_}
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Publications}

\subsection{Peer-reviewed Papers}

\begin{EntriesTable}
  \Year{2022} &
  \Hao, Pi, D-H, Jiang, S-Y, Mao, J, Xu, L, Yang, X, \Weid, \Me, Li, L, \Kurt, \Jamie,
  Mineral paragenesis in Paleozoic manganese ore deposits: Depositional versus post-depositional formation processes,
  \emph{Geochimica et Cosmochimica Acta}, 325, 65–86.
  \DOI{10.1016/j.gca.2022.03.030}
  \\
  ~ &
  \Weid, Chen, N, Sun, W, \Me, \Arps, Teitler, Y, Somelar, P, \Jamie, Babechuk, MG, \Noah, \Dan, \Kurt,
  Binding and transport of Cr(III) by clay minerals during the Great Oxidation Event,
  \emph{Earth and Planetary Science Letters} 584, 117503.
  \DOI{10.1016/j.epsl.2022.117503}
  \\
  ~ &
  \Me, \Noah, \Sus, \Jamie, Wang, C, \Tim, \Kart, \Parn, \Sasha, \Yul, \Arps, \Aivo, \Kurt,
  Chromium evidence for protracted oxygenation during the Paleoproterozoic,
  \emph{Earth and Planetary Science Letters} 584, 117501.
  \DOI{10.1016/j.epsl.2022.117501}
  \Preprint{10.31223/X5NP6G}
  \\
  ~ &
  Soomer, S, Somelar, P, \Me, \Aivo, \Arps,
  Geochemistry and mineralogy of Paleoproterozoic metasediments in the Imandra-Varzuga Greenstone Belt: Implications for sediment provenance, tectonic settings and weathering intensity at the transition to oxygenated surface environments,
  \emph{Precambrian Research} 371, 106578.
  \DOI{10.1016/j.precamres.2022.106578}
  \\
  ~ &
  \Dylan, \Kim, \Stef, \Me, \Kurt, Grandin, P, \Mark,
  Evaporative silicification in floating microbial mats: patterns of oxygen production and preservation potential in silica-undersaturated streams, El Tatio, Chile,
  \emph{Geobiology} 20, 310–330.
  \DOI{10.1111/gbi.12476}
  \\
  \Year{2021} &
  \Me, \Jamie, \Noah, Bekker, A, \Kurt,
  Iron Formations as Palaeoenvironmental Archives,
  \emph{Elements in Geochemical Tracers in Earth System Science}, Cambridge University Press.
  \DOI{10.1017/9781108993791}
  \\
  ~ &
  Zhang, Y, Li, J, Chen, L, Wei, Y, Shi, Q, Wang, D-G, Wu, Q-M, Song, L-Y, Tian, M, Kuang, H-W, Liu, Y-Q, \Me, Bai, H-Q, Liu, Z-L, Wang, Y-C, Qiao, D-W, Zhu, W-J,
  Manganese carbonate stromatolites of the Ediacaran Doushantuo Formation in Chengkou, northern Yangtze Craton, China,
  \emph{Journal of Palaeogeography} 10, 22.
  \DOI{10.1186/s42501-021-00099-9}
  \\
  ~ &
  Farrell, ÚC..., \Me..., \Noah, Lau, KV, Johnston, DT, Sperling, EA,
  The Sedimentary Geochemistry and Paleoenvironments Project,
  \emph{Geobiology} 19, 545–556.
  \DOI{10.1111/gbi.12462}
  \\
  ~ &
  Tong, X, Wang, C, Peng, Z, Li, Y, \Weid, \Me, \Jamie, Zhang, L, Ke, Q, Zhai, M, \Kurt,
  Depositional and Environmental Constraints on the Late Neoarchean Dagushan Deposit (Anshan-Benxi Area, North China Craton): An Algoma-Type Banded Iron Formation,
  \emph{Economic Geology} 116, 1575–1597.
  \DOI{10.5382/econgeo.4841}
  \\
  ~ &
  Shen, F, Yue, L, Liu, Z, Yang, W, \Me, Jin, H, Li, F, Zhou, Y, Zhang, M, Jiang, R,
  Heterogeneity of tight sandstone reservoirs based on fractal theory: the Xu-6 member of Xujiahe Formation in Guang’an area, central Sichuan Basin,
  \emph{Arabian Journal of Geosciences} 14, 1515.
  \DOI{10.1007/s12517-021-07851-4}
  \\
  ~ &
  Lumiste, K, \Me, \Jake, Stüeken, EE, \Kart, Lang, L, Sepp, H, \Aivo, \Arps,
  Constraining the conditions of phosphogenesis: stable isotope and trace element systematics of Recent Namibian phosphatic sediments,
  \emph{Geochimica et Cosmochimica Acta} 302, 141-159.
  \DOI{10.1016/j.gca.2021.03.022}
  \\
  ~ &
  \Weid, \Me, Li, Y, \Dan, Somelar, P, Moussavou, M, \Sasha, \Aivo, \Arps, \Noah, \Kurt,
  The kaolinite shuttle links the Great Oxidation and Lomagundi events,
  \emph{Nature Communications} 12, 2944.
  \DOI{10.1038/s41467-021-23304-8}
  \GitHub{kaarelmand/hao\_et\_al\_kaolinite\_shuttle}
  \\
  ~ &
  \Weid, \Me, Swaren, L, \Kim, \Stef, \Dylan, \Mark, Wilson, SA, \Dan, \Kurt,
  Trace elemental partitioning on clays derived from hydrothermal muds of the El Tatio Geyser Field, Chile,
  \emph{Journal of Geophysical Research: Solid Earth} 126, e2020JB021422.
  \DOI{10.1029/2020JB021422}
  \\
  ~ &
  \Me, \Stef, \Kart, \Marie, Lumiste, K, \Jamie, \Tim, \Sasha, \Arps, \Aivo, \Kurt,
  Iron Isotopes Reveal a Benthic Iron Shuttle in the Palaeoproterozoic Zaonega Formation: Basinal Restriction, Euxinia, and the Effect on Global Palaeoredox Proxies,
  \emph{Minerals} 11, 368.
  \DOI{10.3390/min11040368}
  \\
  ~ &
  Tong, X, \Me, Li, Y, Zhang, L, Peng, Z, Wu, Q, Li, P, Zhai, M, \Jamie, Wang, C, \Kurt,
  Iron and Carbon Isotope Constraints on the Formation Pathway of Iron-Rich Carbonates within the Dagushan Iron Formation, North China Craton,
  \emph{Minerals} 11, 94.
  \DOI{10.3390/min11010094}
  \\
  \Year{2020} &
  \Tim, \Aivo, \Bau, Prave, A, \Kart, \Me, Sepp, H, Martma, T, \Sasha, \Arps,
  Oxygenated conditions in the aftermath of the Lomagundi-Jatuli Event: The carbon isotope and rare earth element signatures of the Paleoproterozoic Zaonega Formation, Russia,
  \emph{Precambrian Research} 347, 105855.
  \DOI{10.1016/j.precamres.2020.105855}
  \\
  ~ &
  \Hao, Pi, D, Jiang, S-Y, \Weid, Cui, H, \Jamie, \Me, Li, L, \Noah, \Kurt,
  Hydrothermally induced 34S enrichment in pyrite as an alternative explanation of the Late-Devonian sulfur isotope excursion in South China,
  \emph{Geochimica et Cosmochimica Acta} 283, 1–21.
  \DOI{10.1016/j.gca.2020.05.017}
  \\
  ~ &
  \Kart, \Aivo, \Aub, \Arps, \Tim, \Me, \Sasha, Rychanchik, DV, \Tony,
  Identifying global vs. basinal controls on Paleoproterozoic organic carbon and sulfur isotope records,
  \emph{Earth-Science Reviews} 207, 103230.
  \DOI{10.1016/j.earscirev.2020.103230}
  \\
  ~ &
  \Hao, Pi, D-H, Jiang, S-Y, \Weid, \Me, \Jamie, Li, L, \Kurt,
  New constraints on the onset age of the Emeishan LIP volcanism and implications for the Guadalupian mass extinction,
  \emph{Lithos} 360–361, 105441.
  \DOI{10.1016/j.lithos.2020.105441}
  \\
  ~ &
  \Me, \Stef, \Jamie, \Marie, \Kart, \Tim, \Parn, \Chris, \Sasha, \Noah, \Arps, \Aivo, \Kurt,
  Palaeoproterozoic oxygenated oceans following the Lomagundi–Jatuli Event,
  \emph{Nature Geoscience} 13, 302–306.
  \DOI{10.1038/s41561-020-0558-5}
  \\
  ~ &
  \Jamie, \Me, \Noah, \Dan, \Kurt,
  Trace Metals,
  \emph{Encyclopedia of Astrobiology}, Springer.
  \DOI{10.1007/978-3-642-27833-4\_5422-1}
  \\
  \Year{2019} &
  Lumiste, K, \Me, \Jake, \Parn, Lang, L, \Aivo, \Arps,
  REE+Y uptake and diagenesis in Recent sedimentary apatites,
  \emph{Chemical Geology} 525, 268–281.
  \DOI{10.1016/j.chemgeo.2019.07.034}
  \\
  ~ &
  Soomer, S, Somelar, P, \Me, Driese, SG, \Aivo, \Arps,
  High-CO2, acidic and oxygen-starved weathering at the Fennoscandian Shield at the Archean-Proterozoic transition,
  \emph{Precambrian Research} 327, 68–80.
  \DOI{10.1016/j.precamres.2019.03.001}
  \\
  \Year{2018} &
  \Kart, \Aivo, \Aub, \Arps, Izon, G, Patel, NK, McLean, F, \Tim, \Me, Bui, TH, \Sasha, Rychanchik, DV, \Tony,
  Multiple sulphur isotope records tracking basinal and global processes in the 1.98 Ga Zaonega Formation, NW Russia,
  \emph{Chemical Geology} 499, 151–164.
  \DOI{10.1016/j.chemgeo.2018.09.025}
  \\
  ~ &
  \Me, \Arps, \Aivo, Crosby, CH, \Jake, \Kurt, Wirth, R, Schreiber, A, Lumiste, K,
  Authigenesis of biomorphic apatite particles from Benguela upwelling zone sediments off Namibia: The role of organic matter in sedimentary apatite nucleation and growth,
  \emph{Geobiology} 16, 640–658.
  \DOI{10.1111/gbi.12309}
  \\
  ~ &
  \Me, Muehlenbachs, K, McKellar, RC, Wolfe, AP, \Kurt,
  Distinct origins for Rovno and Baltic ambers: Evidence from carbon and hydrogen stable isotopes,
  \emph{Palaeogeography, Palaeoclimatology, Palaeoecology} 505, 265–273.
  \DOI{10.1016/j.palaeo.2018.06.004}
  \\
  \Year{2014} &
  \Aivo, Joosu, L, \Arps, \Tony, \Sasha, Črne, AE, Martin, AP, Fallick, AE, Somelar, P, Üpraus, K, \Me, Roberts, NMW, \Mark, Wirth, R, Schreiber, A,
  Potential influence of sulphur bacteria on Palaeoproterozoic phosphogenesis,
  \emph{Nature Geoscience} 7, 20–24.
  \DOI{10.1038/NGEO2005}
  \\
\end{EntriesTable}

\subsection{Non-peer-reviewed Papers}

\begin{EntriesTable}

% Geoloogia sügiskooli kogumiku 2021 eessõna -- https://drive.google.com/file/d/1pYUZcUevOOyS7Y_IVkpP1ZaxPEvJoxH3/view
  \Year{2021} &
  \Me,
  Eessõna [Foreword],
  \emph{Schola Geologica XVII, Vaatame edasi!}, Estonian Naturalists' Society, p. 8.
  \Website{sygiskool.ee/2014/?page\_id=11}
  \\
  \Year{2014} &
  \Me,
  Mikrofossiilid maailma vanimates fosforiitides,
  \emph{Schola Geologica X, Fosfor – aegade algusest tänapäevani}, Estonian Naturalists' Society, pp. 12–15.
  \Website{sygiskool.ee/2014/?page\_id=11}
  \\
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Miscellaneous}

\begin{EntriesTable}
  \Year{2018} &
  Cover image for \textit{Geobiology} journal, volume 16 (2018), issue 6. \newline
  \Website{onlinelibrary.wiley.com/toc/14724669/2018/16/6}
\end{EntriesTable}

\subsection{Affiliations}
\begin{EntriesTable}
  \Duration{2019}{\Ongoing} &
  Geobiology Society
\end{EntriesTable}

\end{document}
